\prop{
    Suppose $\catC$ is a pointed model category. Then any diagram isomorphic to a cofiber sequence is a cofiber sequence, 
    and any diagram isomorphic to a fiber sequence is a fiber sequence.
}

\prop{
    Suppose $\catC$ is a pointed model category. Then for any $X\in\catC$, the diagram $*\to X\xrightarrow{\1}X$ together with the trivial coaction 
    of $\Sigma *=*$ on $X$ is a cofiber sequence, and the diagram $X\xrightarrow{\1}X\to*$ together with the trivial action of $\Omega *=*$ on $X$ 
    is a fiber sequence.
}

\prop{
    Suppose $\catC$ is a pointed model category. Then for any $f:X\to Y\in\Ho\catC$, there exists a cofiber sequnce $X\xrightarrow{f}Y\to Z$, 
    and there exists a fiber sequnce $W\to X\xrightarrow{f}Y$.
}

\prop{
    Suppose $\catC$ is a pointed model category. For any cofiber sequence $X\xrightarrow{f}Y\xrightarrow{g}Z$, the sequence 
    $Y\xrightarrow{g}Z\xrightarrow{\p}\Sigma X$ is a cofiber sequence, where the coaction is given by 
    $$\Sigma X\xrightarrow{m}\Sigma X\amalg\Sigma X\xrightarrow{\1\amalg\Sigma f}\Sigma X\amalg\Sigma Y\xrightarrow{\1\amalg i}\Sigma X\amalg\Sigma Y,$$
    where $m$ is the comultiplication and $i$ is the coinverse. Dually for any fiber sequence $X\xrightarrow{f}Y\xrightarrow{g}Z$, the sequence 
    $\Omega Z\xrightarrow{\p}X\xrightarrow{f}Y$ is a fiber sequence, where the action is given by 
    $$\Omega Z\times\Omega Y\xrightarrow{\1\times i}\Omega Z\times\Omega Y\xrightarrow{\1\times\Omega g}\Omega Z\times\Omega Z\xrightarrow{m}\Omega Z,$$ 
    where $m$ is the multiplication and $i$ is the inverse.
}

\prop{
    Suppose $\catC$ is a pointed model category. If we have a commutative diagram in $\Ho\catC$ as follows:
    $$\xymatrix{
    X\ar[r]^f\ar[d]_\alpha&Y\ar[r]^g\ar[d]_\beta&Z\\
    X'\ar[r]^{f'}&Y'\ar[r]^{g'}&Z'
    }$$
    where the two rows are cofiber sequences, then there exists a map $\gamma:Z\to Z'$ making the following diagram commutative:
    $$\xymatrix{
    X\ar[r]^f\ar[d]_\alpha&Y\ar[r]^g\ar[d]_\beta&Z\ar[r]\ar[d]_\gamma&Z\amalg\Sigma X\ar[d]^{\gamma\amalg\Sigma\alpha}\\
    X'\ar[r]^{f'}&Y'\ar[r]^{g'}&Z'\ar[r]&Z'\amalg\Sigma X'
    }$$
    Dually if we have a commutative diagram in $\Ho\catC$ as follows:
    $$\xymatrix{
    X\ar[r]^f&Y\ar[r]^g\ar[d]^\beta&Z\ar[d]^\alpha\\
    X'\ar[r]^{f'}&Y'\ar[r]^{g'}&Z'
    }$$
    where the two rows are fiber sequences, then there exists a map $\gamma:X\to X'$ making the following diagram commutative:
    $$\xymatrix{
    X\times\Omega Z\ar[r]\ar[d]_{\gamma\times\Omega\alpha}&X\ar[r]^f\ar[d]^\alpha&Y\ar[r]^g\ar[d]^\beta&Z\ar[d]^\alpha\\
    X'\times\Omega Z'\ar[r]&X'\ar[r]^{f'}&Y'\ar[r]^{g'}&Z'
    }$$
}

\prop{
    Suppose $\catC$ is a pointed model category. If $v:X\to Y,u:Y\to Z$ are maps in $\Ho\catC$, then there exists cofiber sequences
    $$X\xrightarrow{v}Y\xrightarrow{d}U,\quad X\xrightarrow{uv}Z\xrightarrow{a}V,\quad Y\xrightarrow{u}Z\xrightarrow{f}W,\quad
     U\xrightarrow{r}V\xrightarrow{s}W,$$
    such that the following diagram is commutative:
    $$\xymatrix{
    X\ar[r]^v\ar[d]_{\1}&Y\ar[r]^d\ar[d]_u&U\ar[r]\ar[d]_r&U\amalg\Sigma X\ar[d]^{r\amalg\1}\\
    X\ar[r]^{uv}\ar[d]_v&Z\ar[r]^a\ar[d]_{\1}&V\ar[r]\ar[d]_s&V\amalg\Sigma X\ar[d]^{s\amalg\Sigma v}\\
    Y\ar[r]^u&Z\ar[r]^f&W\ar[r]\ar[d]&W\amalg\Sigma Y\ar[ld]^{\1\amalg\Sigma d}\\
    &&W\amalg\Sigma U&
    }$$
    Dually there is a statement for fiber sequences.
}

\prop{
    Suppose $\catC$ is a pointed model category, $X\xrightarrow{f}Y\xrightarrow{g}Z$ is a cofiber sequence, $X'\xrightarrow{i}Y'\xrightarrow{p}Z'$ 
    is a fiber sequence. If we have a commutative diagram as follows:
    $$\xymatrix{
    X\ar[r]^f\ar[d]_\alpha&Y\ar[r]^g\ar[d]_\beta&Z\ar[r]^\p&\Sigma X\ar[d]^{-\vp^{-1}\alpha}\\
    \Omega Z'\ar[r]^\p&X'\ar[r]^i&Y'\ar[r]^p&Z'
    }$$
    where $\vp$ is the natural isomorphism $[\Sigma X,Z]\cong[X,\Omega Z]$ and the negative sign is taken with respect to the group structure of
    $[\Sigma X,Z]$, then there exists a fill-in map $\gamma:Z\to Y'$ making the diagram commutative. Dually if we have a commutative diagram as follows:
    $$\xymatrix{
    X\ar[r]^f\ar[d]_{-\vp\delta}&Y\ar[r]^g&Z\ar[r]^\p\ar[d]^\gamma&\Sigma X\ar[d]^\delta\\
    \Omega Z'\ar[r]^\p&X'\ar[r]^i&Y'\ar[r]^p&Z'
    }$$
    then there exists a fill-in map $\beta:Y\to X'$ making the diagram commutative.
}

\prop{
    Suppose $(F,G):\catC\to\catD$ is a Quillen adjunction between pointed model categories. Then $LF:\Ho\catC\to\Ho\catD$ maps any cofiber sequence
    $X\xrightarrow{f}Y\xrightarrow{g}Z$ to a cofiber sequence $LFX\xrightarrow{LFf}LFY\xrightarrow{LFg}LFZ$, where the coaction is given by
    $$LFZ\to LF(Z\amalg\Sigma X)\cong LFZ\amalg LF\Sigma X\xrightarrow{\1\amalg\mu^{-1}}LFZ\amalg\Sigma LFX,$$ where $\mu$ is the structure isomorphism 
    $(LFX)\ov^LS^1\cong LF(X\ov^LS^1)$ of $LF$ as a $\Ho\cat{SSet}_*$-module functor. Dually $RG:\Ho\catD\to\Ho\catC$ maps any fiber sequence 
    $X\xrightarrow{f}Y\xrightarrow{g}Z$ to a fiber sequence $RGX\xrightarrow{RGf}RGY\xrightarrow{RGg}RGZ$, where the action is given by 
    $$RGX\times\Omega RGZ\xrightarrow{\1\times\9\mu^\op\0^{-1}}RGX\times RG\Omega Z\cong RG(X\times\Omega Z)\to RGX,$$
    where $\mu^\op$ is the dual natural transformation of $\mu$.
}

\prop{
    Suppose $\catC$ is a pointed model category. Then for any $A\in\Ho\catC$, $A\ov^L-$ maps cofiber sequences in $\Ho\cat{SSet}_*$ 
    into cofiber sequences in $\Ho\catC$, $A_{*R}^-$ maps cofiber sequences in $\Ho\cat{SSet}_*$ into fiber sequences in $\Ho\catC$, 
    $R\Map_*(-,A)_l\cong R\Map_*(-,A)_r$ maps fiber sequences in $\Ho\catC$ into fiber sequences in $\Ho\cat{SSet}_*$, 
    $R\Map_*(A,-)_l\cong R\Map_*(A,-)_r$ maps cofiber sequences in $\Ho\catC$ into fiber sequences in $\Ho\cat{SSet}_*$.
}

\lem{\label{tagi}
    Suppose $\catC$ is a pointed model category, $f:A\to B$ is a cofibration of cofibrant objects with cofiber $g:B\to C$. Take a cylinder object
    $A'$ of $A$, and define $r:A'\to A''$ to be the cofiber of $A\amalg A\xrightarrow{(i_0,i_1)}A'$. Define $\tilde{B}$ to be the pushout of the diagram:
    $$\xymatrix{A\amalg A\ar[r]^{(i_0,i_1)}\ar[d]_{f\amalg f}&A'\ar[d]\\B\amalg B\ar[r]&\tilde{B}}$$ and factor the map 
    $(f\sigma,\1\amalg\1):\tilde{B}\to B$ into a cofibration $\tilde{B}\to B'$ and a trivial fibration $\sigma:B'\to B$. 
    Then $B'$ is a cylinder object of $B$, and it induces a map $f':A'\to B'$ commuting with $i_0,i_1,\sigma$.
    Let $B_f$ to be the pushout of the diagram: $$\xymatrix{A\ar[r]^{i_0}\ar[d]_f&A'\ar[d]\\B\ar[r]^f&B_f}$$ 
    Then the following diagram is a pushout square: $$\xymatrix{A\ar[r]^{i_1}\ar[d]_{jf}&A'\ar[d]\\B_f\ar[r]&\tilde{B}}$$ Let $\tilde{C}$ to be 
    the pushout of the diagram: $$\xymatrix{B_f\ar[r]^{(i_0,f')}\ar[d]_{(g,r)}&B'\ar[d]^k\\Cof\amalg A''\ar[r]^\pi&\tilde{C}}$$ then $\pi$ 
    is a weak equivalence, and $ki_1f=0:A\to\tilde{C}$, which induces a map $i_1:=(ki_1,0):C\to\tilde{C}$. Take a map $t:A'\to\Cyl A$ 
    commuting with $i_0,i_1,\sigma$, and call the induced map $A''\to A\ov S^1$ also by $t$. Now if we define $\psi:C\to C\amalg\Sigma A$ 
    to be the composite in $\Ho\catC$:
    $$C\xrightarrow{i_1}\tilde{C}\xrightarrow{\pi^{-1}}C\amalg A''\xrightarrow{\1\amalg t}C\amalg(A\ov S^1)\cong C\amalg(QA\ov QS^1)=C\amalg\Sigma A,$$ 
    then $\psi$ coincides with the right coaction given in Theorem \ref{tagh}. Dually there is a statement for fibration of fibrant objects.
}

\lem{
    Suppose $\catC$ is a pointed model category. If $f:A\to B$ is a cofibration of cofibrant objects with cofiber $g:B\to C$, 
    then there exists cosimplicial frames $B^*,C^*$ for $B,C$ and a cofibration $f^*:A^\circ\to B^*$ in $\catC^\d$ covering $f$ with cofiber 
    $g^*:B^*\to C^*$ covering $g$. Dually if $p:E\to B$ is a fibration of fibrant objects with fiber $i:F\to E$, then there exists simplicial frames 
    $F_*,E_*$ for $F,E$ and a fibration $p_*:E_*\to B_\circ$ in $\catC^{\d^\op}$ covering $p$ with fiber $i_*:F_*\to E_*$
    covering $i$.
}

\prop{
    Suppose $\catC,\catD$ are pointed model categories. Then any functor between $\catC$ and $\catD$ preserving cofibrations, weak equivalence 
    between cofibrant objects and colimits preserves cofiber sequences, where the coaction is simply given by acting the functor on the map 
    $\psi$ given in Lemma \ref{tagi}, and any functor between $\catC$ and $\catD$ preserving fibrations, weak equivalence between fibrant objects 
    and limits preserves fiber sequences, where the action is simply given by acting the functor on the map
    given in the dual statement in Lemma \ref{tagi}.
}

\prop{
    Suppose $\catC$ is a pointed model category. Then for any $K\in\cat{SSet}_*$, $-\ov^LK$ maps a cofiber sequence $X\xrightarrow{f}Y\xrightarrow{g}Z$
    in $\Ho\catC$ into a cofiber sequence $X\ov^LK\xrightarrow{f\ov^L\1}Y\ov^LK\xrightarrow{g\ov^L\1}Z\ov^LK$ in $\Ho\catC$, where the coaction
    is given by $$\begin{aligned}&Z\ov^LK\to(Z\amalg\Sigma X)\ov^LK\\&\hspace{0.8em}\cong Z\ov^LK\amalg\Sigma X\ov^LK
    \xrightarrow{\1\amalg\mu^{-1}}Z\ov^LK\amalg\Sigma(X\ov^LK),\end{aligned}$$ where $\mu$ is the structure isomorphism 
    $(X\ov^LK)\ov^LS^1\cong(X\ov^LS^1)\ov^LK$ of $-\ov^LK$ as a $\Ho\cat{SSet}_*$-module functor. Dually $-_{*R}^K$ maps a fiber sequence
    $X\xrightarrow{f}Y\xrightarrow{g}Z$ in $\Ho\catC$ into a fiber sequence $X_{*R}^K\xrightarrow{f_{*R}^\1}Y_{*R}^K\xrightarrow{g_{*R}^\1}Z_{*R}^K$ 
    in $\Ho\catC$, where the action is given by $$Z_{*R}^K\times\Omega X_{*R}^K\xrightarrow{\1\times\9\mu^\op\0^{-1}}Z_{*R}^K\times(\Omega X)_{*R}^K
    \cong(Z\times\Omega X)_{*R}^K\to Z_{*R}^K,$$ where $\mu^\op$ is the dual natural transformation of $\mu$.
}