\defn{
    Suppose $\catC$ is a pointed model category. Define the \term{suspension functor} $\Sigma$ to be the functor $-\ov^LS^1:\Ho\catC\to\Ho\catC$, 
    and the \term{loop functor} $\Omega$ to be the functor $-_{*R}^{S^1}:\Ho\catC\to\Ho\catC$.
}

\lem{
    $(\Sigma,\Omega)$ is an adjoint pair.
}

\lem{
    Suppose $\catC$ is a pointed model category. For any $X\in\catC$, $\Sigma X$ is the cofiber of the map $QX\amalg QX\to\Cyl(QX)$, 
    and is naturally isomorphic in $\Ho\catC$ to the cofiber of the map $X\amalg X\to\Cyl X$ if $X$ is cofibrant. Dually for any $X\in\catC$,
    $\Omega X$ is the fiber of the map $\Path(RX)\to RX\times RX$, and is naturally isomorphic in $\Ho\catC$ to the fiber of the map 
    $\Path X\to X\times X$ if $X$ is fibrant.
}

\prop{
    Suppose $\catC$ is a pointed model category, $A$ is cofibrant in $\catC$, $X$ is fibrant in $\catC$. Then for any nonnegative integer $t$ 
    there exists natural isomorphisms $$[A,\Omega^tX]\cong[\Sigma^tA,X]\cong\pi_t\sHom_*(A,X)_l\cong\pi_t\sHom_*(A,X)_r.$$
}

\lem{
    Suppose $\catC$ is a pointed model category, $A$ is cofibrant in $\catC$, $X$ is fibrant in $\catC$. Then any element in $[\Sigma A,X]$ 
    can be represented by a map $k:A\to X^{\d[1]}=\Path X$ such that $p_0k=p_1k=0$, and two such maps $k,k'$ represent the same element in $[\Sigma A,X]$
    if and only if there exists a map $K:A\to X^{\d[1]\times\d[1]}$ such that $p_0^0K=k,p_0^1K=k',p_1^0K=p_1^1K=0$, 
    where $$p_0^0,p_0^1,p_1^0,p_1^1:X^{\d[1]\times\d[1]}\to X^{\d[1]}$$ are induced by the inclusions
    $$\begin{aligned}
    i_0^0:\d[1]\times\{0\}&\to\d[1]\times\d[1],\\
    i_0^1:\d[1]\times\{1\}&\to\d[1]\times\d[1],\\
    i_1^0:\{0\}\times\d[1]&\to\d[1]\times\d[1],\\
    i_1^1:\{1\}\times\d[1]&\to\d[1]\times\d[1],
    \end{aligned} $$ respectively. Dually any element in $[\Sigma A,X]$ can be represented by a map $h:\Cyl A=A\ox\d[1]\to X$ such that $hi_0=hi_1=0$, 
    and two such maps $h,h'$ represent the same element in $[\Sigma A,X]$ if and only if there exists a map $H:A\ox(\d[1]\times\d[1])\to X$ such that 
    $Hi_0^0=h,Hi_0^1=h',Hi_1^0=Hi_1^1=0$, where $$i_0^0,i_0^1,i_1^0,i_1^1:A\ox\d[1]\to A\ox(\d[1]\times\d[1])$$ are induced by the inclusions given above.
}

\lem{
    Suppose $\catC$ is a pointed model category, $A$ is cofibrant in $\catC$, $X$ is fibrant in $\catC$. Then two maps $k,k':A\to\Path X$ with 
    $p_0k=p_1k=p_0k'=p_1k'=0$ represent the same element in $[\Sigma A,X]$ if and only if there exists a map $K:\Cyl A\to\Path X$ such that 
    $p_0K=p_1K=0,Ki_0=k,Ki_1=k'$. Dually two maps $h,h':\Cyl A\to X$ with $hi_0=hi_1=h'i_0=h'i_1=0$ represent the same element in $[\Sigma A,X]$ 
    if and only if there exists a map $H:\Cyl A\to\Path X$ such that $p_0H=h,p_1H=h',Hi_0=Hi_1=0$.
}

\lem{
    Suppose $\catC$ is a pointed model category, $A$ is cofibrant in $\catC$, $X$ is fibrant in $\catC$. Then two maps $k:A\to\Path X$ with $p_0k=p_1k=0$
    and $h:\Cyl A\to X$ with $hi_0=hi_1=0$ represent the same element in $[\Sigma A,X]$ if and only if there exists a map $H:\Cyl A\to\Path X$ such that 
    $p_0H=h,p_1H=0,Hi_0=k,Hi_1=0$. Such $H$ is called a \term{correspondence} between $h$ and $k$.
}

\cor{
    Suppose $\catC$ is a pointed model category. Then for any $X$ and positive integer $t$, $\Sigma^tX$ is naturally a cogroup object in $\Ho\catC$ 
    that is naturally abelian if $t\ge 2$. Dually $\Omega^tX$ is naturally a group object in $\Ho\catC$ that is naturally abelian if $t\ge 2$.
}

\rmk{
    Suppose $\catC$ is a pointed model category, $A$ is cofibrant in $\catC$, $X$ is fibrant in $\catC$. Then the group structure on $[\Sigma A,X]$ 
    may be expressed as follows: for any $k,k':A\to\Path X$ with $p_0k=p_1k=p_0k'=p_1k'=0$ representing elements in $[\Sigma A,X]$, define $K$ 
    to be a lift of the following diagram:
    $$\xymatrix @C=70pt{
	{*}\ar[d]\ar[r]&X^{\d[2]}\ar[d]\\
	A\ar[r]^{k\text{ on }X^{\d\{0,1\}}}_{k'\text{ on }X^{\d\{1,2\}}}\ar@{.>}[ur]^{K}&X^{\l^1[2]}
    }$$
    then $[k]\cdot[k']=[X^{d_1}K]$; define $H$ to be a lift of the following diagram:
    $$\xymatrix @C=70pt{
	{*}\ar[d]\ar[r]&X^{\d[2]}\ar[d]\\
	A\ar[r]^{k\text{ on }X^{\d\{0,1\}}}_{0\text{ on }X^{\d\{0,2\}}}\ar@{.>}[ur]^{H}&X^{\l^0[2]}
    }$$
    then $[k]^{-1}=[X^{d_0}H]$.
}

\defn{
    Suppose $\catC$ is a pointed model category, $f:A\to B$ is a cofibration of cofibrant objects with cofiber $g:B\to C$, $X$ is fibrant in $\catC$. 
    Then for any map $h:A\to\Path X$ with $p_0h=p_1h=0$ representing an element in $[\Sigma A,X]$ and map $u:C\to X$ representing an element in $[C,X]$, 
    take $\alpha$ to be a lift of the following diagram:
    $$\xymatrix @C=30pt{
	A\ar[rr]^h\ar[d]_f&& \Path X\ar[d]^{p_0}\\
    B\ar[r]^u\ar@{.>}[urr]^{\alpha}&C\ar[r]^g&X
    }$$
    and take $w$ to be the map induced as follows:
    $$\xymatrix{
	A\ar[rr]^h\ar[rd]^f\ar[dd]&& \Path X\ar[dd]^{p_1}\\
    &B\ar[d]^g\ar[ur]^{\alpha}&\\
    {*}\ar[r]&C\ar@{.>}[r]^w&X
    }$$
    and define $[u]\odot[h]=[w]$. Dually suppose $p:E\to B$ is a fibration of fibrant objects with fiber $i:F\to E$, and $A$ is cofibrant in $\catC$. 
    Then for any map $h:\Cyl A\to B$ with $hi_0=hi_1=0$ representing an element in $[A,\Omega B]$ and map $u:A\to F$ representing an element in $[A,F]$,
    take $\alpha$ to be a lift of the following diagram:
    $$\xymatrix @C=30pt{
	A\ar[r]^u\ar[d]_{i_0}&F\ar[r]^i&E\ar[d]^p\\
    \Cyl A\ar@{.>}[urr]^{\alpha}\ar[rr]^h&&B
    }$$
    and take $w$ to be the map induced as follows:
    $$\xymatrix{
	A\ar@{.>}[r]^{w}\ar[dd]_{i_1}&F\ar[r]\ar[d]_{i}&{*}\ar[dd]\\
    &E\ar[dr]^{p}&\\
    \Cyl A\ar[ur]^{\alpha}\ar[rr]^{h}&&B
    }$$
    and define $[u]\odot[h]=[w]$.
}

\lem{
    Suppose $\catC$ is a pointed model category, $f:A\to B$ is a cofibration of cofibrant objects with cofiber $g:B\to C$. Then there exists 
    cylinder objects $B',C'$ for $B,C$, and maps $\Cyl A\xrightarrow{f'}B'\xrightarrow{g'}C'$, such that $f'$ is a cofibration with cofiber $g'$, 
    the following diagram is commutative:
    $$\xymatrix @C=40pt{
    A\amalg A\ar[r]^{(i_0,i_1)}\ar[d]_{f\amalg f}& \Cyl A\ar[r]^{\sigma}\ar[d]^{f'}&A\ar[d]^{f}\\
    B\amalg B\ar[r]^{(i_0,i_1)}\ar[d]_{g\amalg g}&B'\ar[r]^{\sigma}\ar[d]^{g'}&B\ar[d]^{g}\\
    C\amalg C\ar[r]^{(i_0,i_1)}&C'\ar[r]^{\sigma}&C
    }$$
    and the map $\9B\amalg B\0\amalg_{A\amalg A}\Cyl A\to B'$ is a cofibration. Dually there is a statement for fibration of fibrant objects.
}

\lem{
    Suppose $\catC$ is a pointed model category, $f:A\to B$ is a cofibration of cofibrant objects with cofiber $g:B\to C$, $X$ is fibrant in $\catC$.
    Then the map $\odot:[C,X]\times[\Sigma A,X]\to[C,X]$ is well-defined. Dually suppose $p:E\to B$ is a fibration of fibrant objects
    with fiber $i:F\to E$, and $A$ is cofibrant in $\catC$. Then the map $\odot:[A,F]\times[A,\Omega B]\to[A,F]$ is well-defined.
}

\lem{
    Suppose $\catC$ is a pointed model category, $f:A\to B$ is a cofibration of cofibrant objects with cofiber $g:B\to C$, $X$ is fibrant in $\catC$.
    Then the map $\odot:[C,X]\times[\Sigma A,X]\to[C,X]$ is natural in $X$. Dually suppose $p:E\to B$ is a fibration of fibrant objects with fiber 
    $i:F\to E$, and $A$ is cofibrant in $\catC$. Then the map $\odot:[A,F]\times[A,\Omega B]\to[A,F]$ is natural in $A$.
}

\thm{\label{tagh}
    Suppose $\catC$ is a pointed model category, $f:A\to B$ is a cofibration of cofibrant objects with cofiber $g:B\to C$, $X$ is fibrant in $\catC$.
    Then the map $\odot:[C,X]\times[\Sigma A,X]\to[C,X]$ defines a right $[\Sigma A,X]$-action on $[C,X]$, constructing a right $\Sigma A$-coaction 
    on $C$ in $\Ho\catC$. Dually suppose $p:E\to B$ is a fibration of fibrant objects with fiber $i:F\to E$, and $A$ is cofibrant in $\catC$. 
    Then the map $\odot:[A,F]\times[A,\Omega B]\to[A,F]$ defines a right $[A,\Omega B]$-action on $[A,F]$,
    constructing a right $\Omega B$-action on $F$ in $\Ho\catC$.
}

\prop{
    Suppose $\catC$ is a pointed model category, $f_i:A_i\to B_i$ are cofibrations of cofibrant objects with cofibers $g_i:B_i\to C_i$ for $i=1,2$, 
    $p:A_1\to A_2,q:B_1\to B_2$ are maps in $\catC$ such that $qf_1=f_2p$. Then the induced map $r:C_1\to C_2$ is \term{$\Sigma p$-equivariant} 
    in $\Ho\catC$, namely the following diagram is commutative in $\Ho\catC$:
    $$\xymatrix{
	C_1\ar[r]\ar[d]_{r}&C_1\amalg\Sigma A_1\ar[d]^{r\amalg\Sigma p}\\
    C_2\ar[r]&C_2\amalg\Sigma A_2
    }$$
    Dually there is a statement for fibrations of fibrant objects.
}

\defn{
    Suppose $\catC$ is a pointed model category. A \term{cofiber sequence} in $\Ho\catC$ is a diagram $X\to Y\to Z$ in $\Ho\catC$ 
    together with a right $\Sigma X$-coaction on $Z$ in $\Ho\catC$, such that there exists a commutative diagram in $\Ho\catC$:
    $$\xymatrix{
	X\ar[r]\ar[d]_{p}&Y\ar[r]\ar[d]^{q}&Z\ar[d]^{r}\\
    A\ar[r]^f&B\ar[r]^g&C
    }$$
    such that $f:A\to B$ is a cofibration of cofibrant objects with cofiber $g:B\to C$, $p,q,r$ are isomorphisms and $r$ is $\Sigma p$-equivariant. 
    Dually a \term{fiber sequence} in $\Ho\catC$ is a diagram $X\to Y\to Z$ in $\Ho\catC$ together with a right $\Omega Z$-coaction on $X$ in $\Ho\catC$,
    such that there exists a commutative diagram in $\Ho\catC$:
    $$\xymatrix{
	X\ar[r]\ar[d]_{s}&Y\ar[r]\ar[d]^{t}&Z\ar[d]^{u}\\
    F\ar[r]^i&E\ar[r]^p&B
    }$$
    such that $p:E\to B$ is a fibration of fibrant objects with fiber $i:F\to E$, $s,t,u$ are isomorphisms and $s$ is $\Omega u$-equivariant.
}

\lem{
    Suppose $\catC$ is a pointed model category. For any cofiber sequence or fiber sequence $X\to Y\to Z$, the composite of the two maps is $0$.
}

\defn{
    Suppose $\catC$ is a pointed model category. For any cofiber sequence $X\to Y\to Z$, define the \term{boundary map} $\p:Z\to\Sigma X$ to be 
    the composite $$Z\xrightarrow{\text{coaction}}Z\amalg\Sigma X\xrightarrow{0\amalg\1}\Sigma X.$$ Dually for any fiber sequence $X\to Y\to Z$, 
    define the \term{boundary map} $\p:\Omega Z\to X$ to be the composite $$\Omega Z\xrightarrow{(0,\1)}X\times\Omega Z\xrightarrow{\text{action}}X.$$
}

\lem{
    Suppose $\catC$ is a pointed model category. For any cofiber sequence $X\to Y\to Z$ and $\theta\in[\Sigma X,A]$, $\theta\p=[0]\odot\theta$. 
    Dually for any fiber sequence $X\to Y\to Z$ and $\theta\in[A,\Omega Z]$, $\p\theta=[0]\odot\theta$. 
}