\defn{
    Suppose $(\catS,-\ov-,\Map_*(-,-),-_*^-)$ is a closed $\Ho\cat{SSet}_*$-module. Define the \term{suspension functor} $\Sigma$ to be the functor 
    $-\ov S^1:\catS\to\catS$, and the \term{loop functor} $\Omega$ to be the functor $-_*^{S^1}:\catS\to\catS$.
}

\lem{
    Suppose $\catS$ is a closed $\Ho\cat{SSet}_*$-module. Then for any $X$ and positive integer $t$, $\Sigma^tX$ is naturally a cogroup object 
    in $\catS$ that is naturally abelian if $t\ge 2$. Dually $\Omega^tX$ is naturally a group object in $\catS$ that is naturally abelian if $t\ge 2$.
}

\defn{
    Suppose $\catS$ is a closed $\Ho\cat{SSet}_*$-module. A \term{pre-triangulation} on $\catS$ is a collection of \term{cofiber sequences} 
    or \term{left triangles}, and a collection of \term{fiber sequences} or \term{right triangles}, satisfying the following conditions:
    \begin{enumerate}[i)]
    \item A cofiber sequence is a diagram of the form $X\xrightarrow{f}Y\xrightarrow{g}Z$ with a right $\Sigma X$-coaction on $Z$.
    \item The dual statement of i) holds.
    \item Any diagram isomorphic to a cofiber sequence is a cofiber sequence.
    \item The dual statement of iii) holds.
    \item For any $X$, the diagram $*\to X\xrightarrow{\1}X$ together with the trivial coaction of $\Sigma *=*$ on $X$ is a cofiber sequence.
    \item The dual statement of v) holds.
    \item For any $f:X\to Y$, there exists a cofiber sequnce $X\xrightarrow{f}Y\to Z$.
    \item The dual statement of vii) holds.
    \item For any cofiber sequence $X\xrightarrow{f}Y\xrightarrow{g}Z$, the sequence $Y\xrightarrow{g}Z\xrightarrow{\p}\Sigma X$ is a cofiber sequence, 
    where $\p$ is the map $Z\to Z\amalg\Sigma X\xrightarrow{0\amalg\1}\Sigma X$ and the coaction is given by
    $$\Sigma X\xrightarrow{m}\Sigma X\amalg\Sigma X\xrightarrow{\1\amalg\Sigma f}\Sigma X\amalg\Sigma Y\xrightarrow{\1\amalg i}\Sigma X\amalg\Sigma Y,$$ 
    where $m$ is the comultiplication and $i$ is the coinverse.
    \item The dual statement of ix) holds.
    \item For any commutative diagram as follows:
    $$\xymatrix{
    X\ar[r]^f\ar[d]_\alpha&Y\ar[r]^g\ar[d]_\beta&Z\\
    X'\ar[r]^{f'}&Y'\ar[r]^{g'}&Z'
    }$$
    where the two rows are cofiber sequences, there exists a map $\gamma:Z\to Z'$ making the following diagram commutative:
    $$\xymatrix{
    X\ar[r]^f\ar[d]_\alpha&Y\ar[r]^g\ar[d]_\beta&Z\ar[r]\ar[d]_\gamma&Z\amalg\Sigma X\ar[d]^{\gamma\amalg\Sigma\alpha}\\
    X'\ar[r]^{f'}&Y'\ar[r]^{g'}&Z'\ar[r]&Z'\amalg\Sigma X'
    }$$
    \item The dual statement of xi) holds.
    \item For any maps $v:X\to Y,u:Y\to Z$, there exists cofiber sequences
    $$X\xrightarrow{v}Y\xrightarrow{d}U,\quad X\xrightarrow{uv}Z\xrightarrow{a}V,\quad Y\xrightarrow{u}Z\xrightarrow{f}W,\quad 
    U\xrightarrow{r}V\xrightarrow{s}W,$$
    such that the following diagram is commutative:
    $$\xymatrix{
    X\ar[r]^v\ar[d]_{\1}&Y\ar[r]^d\ar[d]_u&U\ar[r]\ar[d]_r&U\amalg\Sigma X\ar[d]^{r\amalg\1}\\
    X\ar[r]^{uv}\ar[d]_v&Z\ar[r]^a\ar[d]_{\1}&V\ar[r]\ar[d]_s&V\amalg\Sigma X\ar[d]^{s\amalg\Sigma v}\\
    Y\ar[r]^u&Z\ar[r]^f&W\ar[r]\ar[d]&W\amalg\Sigma Y\ar[ld]^{\1\amalg\Sigma d}\\
    &&W\amalg\Sigma U&
    }$$
    \item The dual statement of xiii) holds.
    \item For any cofiber sequence $X\xrightarrow{f}Y\xrightarrow{g}Z$ and fiber sequence $X'\xrightarrow{i}Y'\xrightarrow{p}Z'$ 
    and a commutative diagram as follows:
    $$\xymatrix{
    X\ar[r]^f\ar[d]_\alpha&Y\ar[r]^g\ar[d]_\beta&Z\ar[r]^\p&\Sigma X\ar[d]^{-\vp^{-1}\alpha}\\
    \Omega Z'\ar[r]^\p&X'\ar[r]^i&Y'\ar[r]^p&Z'
    }$$
    where $\vp$ is the natural isomorphism $[\Sigma X,Z]\cong[X,\Omega Z]$ and the negative sign is taken with respect to the group structure 
    of $[\Sigma X,Z]$, there exists a fill-in map $\gamma:Z\to Y'$ making the diagram commutative.
    \item The dual statement of xv) holds.
    \item For any cofiber sequence $X\xrightarrow{f}Y\xrightarrow{g}Z$ in $\catS$ and $K\in\Ho\cat{SSet}_*$, the sequence 
    $X\ov K\xrightarrow{f\ov\1}Y\ov K\xrightarrow{g\ov\1}Z\ov K$ is a cofiber sequence, where the coaction is given by
    $$\begin{aligned}&Z\ov K\to(Z\amalg\Sigma X)\ov K\\&\hspace{0.8em}\cong Z\ov K\amalg\Sigma X\ov K\xrightarrow{\1\amalg\mu^{-1}}
    Z\ov K\amalg\Sigma(X\ov K),\end{aligned}$$
    where $\mu$ is the structure isomorphism $(X\ov K)\ov S^1\cong(X\ov S^1)\ov K$ of $-\ov K$ as a $\Ho\cat{SSet}_*$-module functor.
    \item The dual statement of xvii) holds.
    \item For any cofiber sequence $K\xrightarrow{f}L\xrightarrow{g}M$ in $\Ho\cat{SSet}_*$ and $X\in\catS$, the sequence 
    $X\ov K\xrightarrow{\1\ov f}X\ov L\xrightarrow{\1\ov g}X\ov M$ is a cofiber sequence, where the coaction is given by
    $$\begin{aligned}&X\ov M\to X\ov(M\amalg\Sigma K)\\&\hspace{0.8em}\cong X\ov M\amalg X\ov\Sigma K\xrightarrow{\1\amalg\mu^{-1}}
    X\ov M\amalg\Sigma(X\ov K),\end{aligned}$$ where $\mu$ is the structure isomorphism $(X\ov S^1)\ov K\cong(X\ov K)\ov S^1$ of $-\ov S^1$ 
    as a $\Ho\cat{SSet}_*$-module functor.
    \item The dual statement of xix) holds.
    \item For any fiber sequence $X\xrightarrow{f}Y\xrightarrow{g}Z$ in $\catS$ and $A\in\catS$, the sequence
    $\Map_*(A,X)\xrightarrow{\Map_*(A,f)}\Map_*(A,Y)\xrightarrow{\Map_*(A,g)}\Map_*(A,Z)$ is a fiber sequence, where the action is given by
    $$\begin{aligned}&\Map_*(A,X)\times\Omega\Map_*(A,Z)\xrightarrow{\1\times\mu^\op}\Map_*(A,X)\times\Map_*(A,\Omega Z)\\
    &\hspace{0.8em}\cong\Map_*(A,X\times\Omega Z)\to\Map_*(A,X),\end{aligned}$$
    where $\mu^\op$ is the dual of the structure isomorphism $(A\ov K)\ov S^1\cong A\ov(K\ov^LS^1)$ of $A\ov-$ as a $\Ho\cat{SSet}_*$-module functor.
    \item The dual statement of xxi) holds.
    \end{enumerate}
    A \term{pre-triangulated category} is a closed $\Ho\cat{SSet}_*$-module with all small products and coproducts together with a pre-triangulation.
}

\prop{
    Suppose $\catS$ is a pre-triangulated category.
    \begin{enumerate}[i)]
    \item Suppose $X\xrightarrow{f}Y\xrightarrow{g}Z$ is a cofiber sequence, $W$ is an object. Then there exists a long exact sequences of pointed sets:
    $$\begin{aligned}\cdots\xrightarrow{(\Sigma\p)^*}[\Sigma Z,W]\xrightarrow{(\Sigma g)^*}[\Sigma Y,W]&\xrightarrow{(\Sigma f)^*}[\Sigma X,W]\\
    &\xrightarrow{\p^*}[Z,W]\xrightarrow{g^*}[Y,W]\xrightarrow{f^*}[X,W],\end{aligned}$$
    with the following addition properties:
    \begin{itemize}
    \item For any $a,b\in[Z,W]$, $g^*a=g^*b$ if and only if there is an $x\in[\Sigma X,W]$ such that $a\odot x=b$;
    \item For any $a,d\in[\Sigma X,W]$, $\p^*c=\p^*d$ if and only if there is an $y\in[\Sigma Y,W]$ such that $c\cdot(\Sigma f)^*y=d$.
    \end{itemize} 
    \item Suppose $X\xrightarrow{f}Y\xrightarrow{g}Z$ and $X'\xrightarrow{f'}Y'\xrightarrow{g'}Z'$ are cofiber sequences and we have 
    a commutative diagram as follows:
    $$\xymatrix{X\ar[r]^f\ar[d]_a&Y\ar[r]^g\ar[d]_b&Z\ar[r]\ar[d]_c&Z\amalg\Sigma X\ar[d]^{c\amalg\Sigma a}\\
    X'\ar[r]^{f'}&Y'\ar[r]^{g'}&Z'\ar[r]&Z'\amalg\Sigma X'}$$
    Then if $a,b$ are isomorphisms, so is $c$.
    \end{enumerate} 
    Dually there is a statement for fiber sequences.
}

\defn{
    Suppose $\catS$ and $\catT$ are pre-triangulated categories. A functor $F:\catS\to\catT$ is called a \term{right exact functor} 
    if it is a left adjoint, it is a $\Ho\cat{SSet}_*$-module functor, and it maps any cofiber sequence $X\xrightarrow{f}Y\xrightarrow{g}Z$ 
    to a cofiber sequence $FX\xrightarrow{Ff}FY\xrightarrow{Fg}FZ$, where the coaction is given by
    $$FZ\to F(Z\amalg\Sigma X)\cong FZ\amalg F\Sigma X\xrightarrow{\1\amalg\mu^{-1}}FZ\amalg\Sigma FX,$$ where $\mu$ is the structure isomorphism 
    $(FX)\ov S^1\cong F(X\ov^LS^1)$ of $F$ as a $\Ho\cat{SSet}_*$-module functor. Dually a functor $G:\catT\to\catS$ is called 
    a \term{left exact functor} if it is a right adjoint, its left adjoint is a $\Ho\cat{SSet}_*$-module functor, and it maps any fiber sequence
    $X\xrightarrow{f}Y\xrightarrow{g}Z$ to a cofiber sequence $GX\xrightarrow{Gf}GY\xrightarrow{Gg}GZ$, where the action is given by
    $$GX\times\Omega GZ\xrightarrow{\1\times\9\mu^\op\0^{-1}}GX\times G\Omega Z\cong G(X\times\Omega Z)\to GX,$$ where $\mu^\op$ is 
    the dual natural transformation of the structure isomorphism of its left adjoint as a $\Ho\cat{SSet}_*$-module functor. An adjunction 
    $(F,G):\catS\to\catT$ is called an \term{exact adjunction} if $F$ is right exact and $G$ is left exact.\footnote{The notations here 
    are OPPOSITE from the notations in the original book, since the notations given here coincide with our usual thoughts.}
}

\lem{
    Pre-triangulated categories, exact adjunctions and $\Ho\cat{SSet}_*$-module natural transformations form a 2-category, 
    which we denote $\catt{PreTr}$. There exists a duality 2-functor $-^\op$ on $\catt{PreTr}$.
}

\thm{
    The pseudo-2-functor $$\Ho:\catt{Model}_*\to\catt{CloModule}_{\Ho\cat{SSet}_*}$$ lifts to a pseudo-2-functor $$\Ho:\catt{Model}_*\to\catt{PreTr}.$$
    Moreover $\Ho\circ\9-^\op\0=\9-^\op\0\circ\Ho:\catt{Model}_*\to\catt{PreTr}$.
}

\defn{
    A \term{closed monoidal pre-triangulated category} is a closed $\Ho\cat{SSet}_*$-algebra $(\catS,\ov,i)$ with all small products and coproducts,
    together with a pre-triangulation, such that for any $X\in\catS$, the functors $X\ov-,-\ov X:\catS\to\catS$ are right exact, and the functors
    $\sHom_l(X,-),\sHom_r(X,-):\catS\to\catS,\sHom_l(-,X),\sHom_r(-,X):\catS^\op\to\catS$ are left exact. We define a \term{closed symmetric monoidal 
    pre-triangulated category} to be a closed monoidal pre-triangulated category that is also a closed symmetric $\Ho\cat{SSet}_*$-algebra.
}

\defn{
    For any closed monoidal pre-triangulated category $\catS$, define $S^n=\Sigma^nS=i(S^n)$ for any nonnegative integer $n$.
}

\lem{
    Suppose $\catS$ is a closed symmetric monoidal pre-triangulated category, then the following diagram is commutative for any nonnegative integers $m,n$:
    $$\xymatrix{S^m\ov S^n\ar[r]^\mu\ar[d]_T&S^{m+n}\ar[d]^{(-1)^{mn}\1}\\S^n\ov S^m\ar[r]^\mu&S^{m+n}}$$ where $\mu$ is the structure isomorphism 
    of the monoidal functor $i$ and the negative sign is taken with respect to the cogroup structure of $S^{m+n}$.
}

\defn{
    We define a \term{closed monoidal exact adjunction} between closed monoidal pre-triangulated categories to be an exact adjunction that is also 
    a closed $\Ho\cat{SSet}_*$-algebra functor. A \term{closed symmetric monoidal exact adjunction} between closed monoidal pre-triangulated categories 
    is an exact adjunction that is also a closed symmetric $\Ho\cat{SSet}_*$-algebra functor.
}

\lem{
    Closed monoidal pre-triangulated categories, closed monoidal exact adjunctions and $\Ho\cat{SSet}_*$-algebra natural transformations 
    form a 2-category, which we will denote $\catt{CloMonPreTr}$. Closed symmetric monoidal pre-triangulated categories, closed symmetric monoidal 
    exact adjunctions and $\Ho\cat{SSet}_*$-algebra natural transformations form a 2-category, which we denote $\catt{CloSymMonPreTr}$.
}

\thm{
    The pseudo-2-functor $$\Ho:\catt{MonModel}_*\to\catt{CloAlg}_{\Ho\cat{SSet}_*}$$ lifts to a pseudo-2-functor 
    $$\Ho:\catt{MonModel}_*\to\catt{CloMonPreTr}.$$ The pseudo-2-functor $$\Ho:\catt{SymMonModel}_*\to\catt{CloSymAlg}_{\Ho\cat{SSet}_*}$$ 
    lifts to a pseudo-2-functor $$\Ho:\catt{SymMonModel}_*\to\catt{CloSymMonPreTr}.$$
}