\label{secb}

Although the study of model categories given in Chapter 1 are rather useful, in this chapter we still need to use some more properties
of model categories that we have not discussed yet. Most of these properties are related with enriched categories and presentable categories,
that have been discussed in the previous section. We will discuss these properties in this section.

We start with a lifting criterion:

\prop{
    Suppose $\catC$ is a model category, $i:A\to B$ is a cofibration between cofibrant objects, $X$ is a fibrant object,
    and $f:A\to X$ is a map. If there exists a map $\bar{g}\in[B,X]$ such that $[f]=\bar g[i]$ in $\Ho\catC$, then
    there exists a map $g\in\Hom_\catC(B,X)$ such that $f=gi$.
}

Next we discuss about the stability of weak equivalences under pushouts and pullbacks:

\defn{
    Suppose $\catC$ is a model category. $\catC$ is called \term{left proper}, if weak equivalences is stable under pushouts by cofibrations.
    Dually $\catC$ is called \term{right proper}, if weak equivalences is stable under pullback by fibrations.
}

The following lemma and corollary can be used to deduce whether a category is left proper or not:

\lem{
    In a model category, weak equivalences between cofibrant objects is stable under pushouts by cofibrations.
}

\cor{
    A model category with all objects cofibrant is left proper.
}

The following proposition can be deduced from the previous chapter:

\prop{
    $\cat{SSet}$, with the standard model structure, is right proper.
}

The study of left proper model categories is also related with homotopy pushouts:

\prop{
    Suppose $$\xymatrix{A\ar[r]^i\ar[d]_j&B\ar[d]\\C\ar[r]&B\amalg_AC}$$ is a pushout square in a model category $\catC$.
    If:
    \begin{enumerate}[i)]
        \item Either $A,B$ are cofibrant and $j$ is a cofibration;
        \item Or $\catC$ is left proper and $i$ is a cofibration;
    \end{enumerate}
    Then the square is a homotopy pushout square.
}

The next concept is the study of combinatorial model categories:

\defn{
    A model category is called \term{combinatorial}, if it is presentable and cofibrantly generated.
}

Combinatorial model categories enjoy certain accessibility properties:

\prop{
    Suppose $\catC$ is a combinatorial model category. The full subcategories $\Fib,\W,\W\cap\Fib$ of $\catC^{[1]}$ are accessible.
}

To the converse, given certain accessibilities, one can construct examples of combinatorial model categories:

\lem{[$\dagger$]
    Suppose $\catC$ is a presentable category, $\Cof$ and $\W$ are two classes of morphisms in $\catC$. Suppose more that:
    \begin{enumerate}[i)]
        \item $\Cof$ is a weakly saturated class of morphisms in $\catC$ and is \term{of small generation};
        that is, there exists a set of morphisms $I$ such that $\Cof=\Cof(I)$;
        \item $\Cof\cap\W$ is a weakly saturated class of morphisms;
        \item $\W$ is an accessible full subcategory of $\catC^{[1]}$;
        \item $\W$ has the 2-out-of-3 property.
    \end{enumerate}
    Then $\Cof\cap\W$ is of small generation.
}

\prop{\label{tagq}
    Suppose $\catC$ is a presentable category, $\Cof$ and $\W$ are two classes of morphisms in $\catC$. Suppose more that:
    \begin{enumerate}[i)]
        \item $\Cof$ is a weakly saturated class of morphisms in $\catC$ and is \term{of small generation};
        that is, there exists a set of morphisms $I$ such that $\Cof=\Cof(I)$;
        \item $\Cof\cap\W$ is a weakly saturated class of morphisms;
        \item $\W$ is an accessible full subcategory of $\catC^{[1]}$;
        \item $\W$ has the 2-out-of-3 property;
        \item $\RLP(\Cof)\subseteq\W$.
    \end{enumerate}
    Then $\catC$ admits a combinatorial model structure, with cofibrations being $\Cof$ and weak equivalences being $\W$.
}

\cor{
    Suppose $\catC$ is a presentable model category such that $\Cof$, as a weakly saturated class of morphisms, is of small generation.
    Then the following are equivalent:
    \begin{itemize}
        \item $\catC$ is combinatorial;
        \item $\W$ is an accessible full subcategory of $\catC^{[1]}$.
    \end{itemize}
}

We now present another version of the above proposition that we will frequently use in the following section:

\defn{
    Suppose $\catC$ is a presentable category. A class of morphisms $\W$ in $\catC$ is called \term{perfect},
    if it contains every isomorphism, satisfies the 2-out-of-3 property, and is an $\omega$-accessible full subcatgeory of $\catC^{[1]}$.
}

For example, the class of all isomorphisms in $\catC$ is perfect, whenever $\catC$ is presentable. Also, the class of weak homotopy equivalences
in $\cat{SSet}$ is perfect.

\prop{
    Suppose $F:\catC\to\catD$ is a functor between presentable categories which preserves filtered colimits and 
    $\W$ is a perfect class of morphisms in $\catD$. Then $F^{-1}(\W)$ is a perfect class of morphisms in $\catC$.
}

\prop{\label{tagp}
    Suppose $\catC$ is a presentable category, $\W$ is a class of morphisms in $\catC$, $I$ is a set of morphisms in $\catC$. Suppose more that:
    \begin{enumerate}[i)]
        \item $\W$ is a perfect class of morphisms;
        \item $\W$ is stble under pushouts by pushouts of elements in $I$;
        \item $\RLP(I)\subseteq\W$.
    \end{enumerate}
    Then $\catC$ admits a left proper combinatorial model structure, with cofibrations being $\Cof(I)$ and weak equivalences being $\W$.
}

The next concept is the theory of diagram categories and homotopy limits and colimits. We first make the following definitions:

\defn{
    Suppose $\catI$ is a small category and $\catC$ is a model category. We define a map $\alpha\in\catC^\catI$ to be:
    \begin{enumerate}[i)]
        \item An \term{injective cofibration} if it is a degreewise cofibration;
        \item A \term{projective fibration} if it is a degreewise fibration;
        \item A \term{weak equivalence} if it is a degreewise weak equivalence;
        \item A \term{projective cofibration} if it has LLP with respect to every map that is both a projective fibration and a weak equivalence;
        \item An \term{injective fibration} if it has RLP with respect to every map that is both a injective cofibration and a weak equivalence.
    \end{enumerate}
}

We now state the following proposition:

\prop{
    Suppose $\catC$ is a combinatorial model category, $\catI$ is a small category. Then the projective cofibrations, projective fibrations
    and weak equivalences form a combinatorial model structure on $\catC^\catI$, which will be called the \term{projective model structure},
    denoted $(\catC^\catI,\text{proj})$; the injective cofibrations, injective fibrations
    and weak equivalences form a combinatorial model structure on $\catC^\catI$, which will be called the \term{injective model structure},
    denoted $(\catC^\catI,\text{inj})$.
}

The projective model structure is easy: One can even write down the generating cofibrations and the generating trivial cofibrations.
For any $I\in\catI$ and $C\in\catC$ we define the functor $F_C^I:\catI\to\catC$ by $$F_C^I(I')=\coprod_{\alpha\in\Hom_\catI(I,I')}C.$$
Then, if $I_0$ is the set of generating cofibrations in $\catC$, $\{F_C^I\to F_{C'}^I\mid C\to C'\in I_0,I\in\catI\}$ is the 
set of generating cofibrations in $\catC^\catI$, and similar for the generating trivial cofibrations. The injective model structure 
is more complicated and requires Proposition \ref{tagq}. The following lemma is also needed:

\lem{
    Suppose $\catC$ is a presentable category and $\catI$ be a small category. Suppose $S_0$ is a weakly saturated class of morphisms in
    $\catC$ that is of small generation. Let $S$ be the class of morphisms in $\catC^\catI$ that degreewise belongs to $S_0$.
    Then $S$ is a weakly saturated class of morphisms that is of small generation.
}

We note that if $\catC$ is left or right proper, then the projective model structure and the injective model structure on $\catC^\catI$ 
are left or right proper, respectively. Also note that every projective cofibration is an injective cofibration, and every
injective fibration is a projective fibration.

The projective model structure and the injective model structure are functorial in $\catC$. Namely, if $(F,G):\catC\to\catD$ is a 
Quillen adjunction between combinatorial model categories, then $$(F^\catI,G^\catI):(\catC^\catI,\text{proj})\to(\catD^\catI,\text{proj})$$
and $$(F^\catI,G^\catI):(\catC^\catI,\text{inj})\to(\catD^\catI,\text{inj})$$ are Quillen adjunctions, that are Quillen equivalences 
if $(F,G)$ is one.

The projective and injective model structures are also functorial in $\catI$ in the following sense:

\prop{
    Suppose $f:\catI\to\catJ$ is a functor between small categories, $\catC$ is a combinatorial model category. Then:
    \begin{enumerate}[i)]
        \item The adjunction $(f_!,f^*):(\catC^\catI,\text{proj})\to(\catC^\catJ,\text{proj})$ is a Quillen adjunction;
        \item The adjunction $(f^*,f_*):(\catC^\catJ,\text{inj})\to(\catC^\catI,\text{inj})$ is a Quillen adjunction.
    \end{enumerate}
    Both adjunctions are Quillen equivalences if $f$ is an equivalence between categories.
}

We now discuss homotopy limits and colimits. Since the concepts are dual to each other we only give discussions to homotopy limits,
leaving the dual statements for the reader. 

\defn{
    Suppose $\catC$ is a combinatorial model category, $f:\catI\to\catJ$ is a functor between small categories, $F:\catI\to\catC$
    is a functor. A \term{homotopy right Kan extension of $F$} consists of a functor $G:\catJ\to\catC$ and a natural transformation
    $G\to f_*F$, such that the composition $G\to f_*F\to f_*RF$ is a weak equivalence, where $R$ is the fibrant replacement functor
    with respect to the injective model structure.
}

Note that a homotopy right Kan extension, if exists, is unique up to weak equivalences.

\defn{
    Suppose $\catC$ is a combinatorial model category, $\catI$ is a small category, $F:\catI\to\catC$ is a functor. 
    A \term{homotopy limit} of $F$ is a homotopy right Kan extension of $F$ along the map $\catI\to[0]$.
}

One can show that, as an example, homotopy pullback squares are a special type of homotopy limits.

The following proposition reduce the study of homotopy right Kan extensions to the study of homotopy limits:

\prop{
    Suppose $\catC$ is a combinatorial model category, $f:\catI\to\catJ$ is a functor between small categories, $F:\catI\to\catC$
    is a functor. A natural transformation $G\to f_*F$ exhibits $G$ as a homotopy right Kan extension of $F$, if and only if
    for every $a\in\catJ$, the natural transformation exhibits $G(a)$ as a homotopy limit of $F:\catI\times_{\catJ}\catJ_{a/}\to\catC$.
}

We now focus on enriched homotopy theory and enriched model categories. The reason we discuss enriched homotopy theory, is that even though
our main model for $(\infty,1)$-categories is the theory of quasi-categories, the theory of simplicial categories is also used very often. 
Enriched homotopy theory, though not being introduced in this lecture, can also be viewed as models of other higher category theory, such as 
the $(\infty,2)$-categories, with the model being $(\cat{SSet},\text{Joyal})$-enriched categories. In the remaining of this section, we fix 
a symmetric monoidal model category $\catS$ as the base of our enrichment, and we will be adding more assumptions on $\catS$ as we discuss further.
Note that in the following discussions, it is also available to set $\catS$ to be the trivial model structure on $\cat{Set}$, which will reduce
to the study of ordinary model categories and the homotopy theory of the category of categories.

We first discuss the model structure on the category of $\catS$-enriched categories.

\defn{
    For a $\catS$-enriched category $\catC$, we define $\h\catC$ to be the $\Ho\catS$-enriched category under the map $\catS\to\Ho\catS$.
    A map $F:\catC\to\catD$ between $\catS$-enriched categories is called a \term{weak equivalence} if $\h F:\h\catC\to\h\catD$
    is fully faithful and essentially surjective.
}

Note that whenever the weak equivalences in $\catS$ is stable under filtered colimits, the weak equivalences in $\cat{Cat}_{\catS}$
is stable under filtered colimits. If moreover $\catS$ is a combinatorial model category, then the weak equivalences in $\cat{Cat}_{\catS}$
is a perfect class of morphisms.

Next, we make the following definition:

\defn{
    For any $S\in\catS$ we define the $\catS$-enriched category $[1]_S$ to be the category with two objects $0,1$ and 
    $$\Hom_{[1]_S}(0,0)=\Hom_{[1]_S}(1,1)=\1_{\catS},\Hom_{[1]_S}(0,1)=S,\Hom_{[1]_S}(1,0)=\varnothing.$$ We define $[0]_{\catS}$ or $[0]$
    to be the $\catS$-enriched category with only one object $0$ and its endomorphism space $\1_{\catS}$.
    We define $I_0$ to be the set of morphisms $$\{\varnothing\to[0]\}\cup\{[1]_A\to[1]_B\mid A\to B\text{ is a generating cofibration}\}.$$
}

\tbc

% To be added: Enriched homotopy theory